Rarefied Null Models

### 2021-09-16 analysis/02_rarefy_timeseries.Rmd
more intuitive variable names

##	Get trait filtered data, rename colums to jive with the rest of the script
bt_grid_filtered <- pins::pin_get("bt-traitfiltered", board = "github") %>%
  rename_with(toupper) %>%
  rename(Species = SPECIES, StudyMethod = STUDYMETHOD, ObsEventID = OBSEVENTID,
         rarefyID = RAREFYID, cell = CELL, Abundance = ABUNDANCE, Biomass = BIOMASS)

@@

Get rarefied diversity metrics
```{r}
## Separate true abundance (count) data from presence and biomass/cover data
bt_grid_abund <- bt_grid_filtered %>%
  filter(ABUNDANCE_TYPE %in% c("Count", "Density", "MeanCount"))

bt_grid_pres <- bt_grid_filtered %>%
  filter(ABUNDANCE_TYPE == "Presence/Absence")

>>>>

##	Get trait filtered data, rename colums to jive with the rest of the script
bt_traitfiltered <- pins::pin_get("bt-traitfiltered", board = "github") %>%
  rename_with(toupper) %>%
  rename(Species = SPECIES, StudyMethod = STUDYMETHOD, ObsEventID = OBSEVENTID,
         rarefyID = RAREFYID, cell = CELL, Abundance = ABUNDANCE, Biomass = BIOMASS)

@@

Get rarefied diversity metrics
```{r}
## Separate true abundance (count) data from presence and biomass/cover data
bt_grid_abund <- bt_traitfiltered %>%
  filter(ABUNDANCE_TYPE %in% c("Count", "Density", "MeanCount"))

bt_grid_pres <- bt_traitfiltered %>%
  filter(ABUNDANCE_TYPE == "Presence/Absence")

### 2021-09-16 analysis/03_rarefy_null_models.Rmd
more intuitive variable names

Get dataframe of filenames and corresponding rarefyID's
```{r}
path <- here::here("data", "rarefied_samples")
files <- list.files(path) %>%
  paste0(path, "/", .)

# samples <- purrr::map_dfr(files, function(x) {load(x)
#   return(rare_comm_save)
# 	}) %>% distinct()
```

Function to get all rarefied samples for an ID
```{r}
# get_rarefy_samps <- function(id, path = here::here("data", "rarefied_samples")){
#   print(id)
#   samp_data <- list.files(path = path, pattern = paste0( "*.", id, ".*")) %>% 
#     paste0(path, "/", .) %>%
#      purrr::map_dfr(., function(x) {load(x)
#        return(rare_comm_save)
#        }) 
#   return(samp_data)
# }
```
Get species pools for each timeseries
```{r}
bt_grid_filtered <- pins::pin_get("bt-traitfiltered", board = "github")
trait_ref <- pins::pin_get("trait-ref", board = "github")

species_pools <- bt_grid_filtered %>%
  select(rarefyid, species) %>% 
  distinct()

rm(bt_grid_filtered)
```

>>>>

Get dataframe of filenames and corresponding rarefyID's
```{r}
path <- here::here("data", "rarefied_samples")
files <- list.files(path) %>%
  paste0(path, "/", .)
```

Get species pools for each timeseries
```{r}
bt_traitfiltered <- pins::pin_get("bt-traitfiltered", board = "github")
trait_ref <- pins::pin_get("trait-ref", board = "github")

species_pools <- bt_traitfiltered %>%
  select(rarefyid, species) %>% 
  distinct()

rm(bt_traitfiltered)
```
